\documentclass[11pt,a4paper]{article}

\usepackage[margin=2.4cm]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{booktabs}
\usepackage{array}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{listings}

\hypersetup{colorlinks=true, linkcolor=blue!50!black, urlcolor=blue!60!black}
\lstset{
  basicstyle=\ttfamily\small,
  frame=single,
  breaklines=true,
  columns=fullflexible,
  backgroundcolor=\color{black!3}
}

\title{Personalized Static Hand-Gesture Recognition\\
\large Classical Machine-Learning Models Compared with Geometric Rules}
\author{Gesture Presenter --- Machine Learning Course Study}
\date{13 July 2026}

\begin{document}
\maketitle

\begin{abstract}
This report presents a personalized, single-participant pilot study built on
Gesture Presenter, a desktop presentation controller based on MediaPipe hand
landmarks. The study asks whether a lightweight and explainable classical
machine-learning model can classify the participant's static gestures more
accurately than the application's manually designed geometric rules. Camera
frames were processed locally and were not saved; only 21 three-dimensional
hand landmarks and experimental metadata were recorded. A class-balanced
decision tree, random forest, and logistic regression model were trained on two
recording sessions and evaluated on a held-out third session. The random forest
performed best, reaching 98.8\% frame-level and 98.5\% trial-level accuracy.
Logistic regression achieved 95.7\% and 94.8\%, the single tree achieved 91.7\%
and 93.3\%, and the hard-coded rules achieved 80.0\% and 79.3\%. The largest
practical difference was rejection of non-command movement: every learned model
performed substantially better than the rules, and the tree recognized every
held-out
\texttt{none} trial, whereas the rules recognized none of them. The result
supports the feasibility of personalized learned gesture boundaries, but it
does not establish generalization to other users or action-level superiority in
the live product.
\end{abstract}

\section{System context}

Gesture Presenter converts hand movements into presentation actions such as
pointer movement, clicks, scrolling, slide changes, and media control. Its
recognition pipeline has two distinct parts:
\begin{enumerate}
  \item MediaPipe Hand Landmarker detects a hand and returns 21 landmarks, each
        with normalized $x$, $y$, and $z$ coordinates.
  \item Application-specific logic maps those landmarks to gestures and then
        uses temporal state machines to dispatch actions.
\end{enumerate}

The production gesture classifier is not a learned classifier. It applies
manually chosen conditions to joint angles, normalized fingertip distances,
finger-extension states, thumb direction, and finger gaps. For example, an
index pinch is identified through the normalized distance between the thumb and
index fingertips, with separate closing and opening thresholds to provide
hysteresis. This rule system is understandable and efficient, but universal
thresholds may not match one user's hand shape and gesture style.

\section{Research goal}

The central question was:

\begin{quote}
Can a lightweight, explainable classical machine-learning model improve static
gesture classification for one user across separate recording sessions when
compared with the existing hand-written geometric classifier?
\end{quote}

The experiment was intentionally framed as a \emph{personalized pilot}. With
one participant and one evening available for data collection, it would not be
valid to claim population-level or cross-user generalization. The goals were
instead to:
\begin{itemize}
  \item test whether learned boundaries adapt better to the participant;
  \item compare both classifiers on identical, held-out landmark observations;
  \item preserve interpretability for later explainable-AI analysis;
  \item identify gesture classes and failure modes requiring further work; and
  \item establish a reproducible research workflow without changing the
        end-user application.
\end{itemize}

\section{Data collection}

\subsection{Guided collection procedure}

A separate playground script guided the participant through randomized gesture
trials. For each trial, the interface displayed the target gesture, a countdown,
a 1.5-second recording interval, and a rest interval. The nominal protocol used
15 repetitions of each of nine classes, producing 135 prompted trials per
session. The participant used the right hand, which is the presentation-control
hand in the product.

The nine labels were:
\begin{center}
\begin{tabular}{lll}
\toprule
\texttt{none} & \texttt{point} & \texttt{pinch} \\
\texttt{pinch\_right} & \texttt{open\_palm} & \texttt{fist} \\
\texttt{fist\_thumb\_up} & \texttt{v\_sign} & \texttt{two\_finger\_scroll} \\
\bottomrule
\end{tabular}
\end{center}

The \texttt{none} class represented natural hand motion without an intended
command. It is especially important in an interaction system: a classifier that
performs well only on carefully posed commands may still trigger actions during
ordinary movement.

Three sessions were recorded. Sessions \texttt{S01} and \texttt{S02} formed the
training data. Session \texttt{S03} was excluded during training and reserved
for the final comparison.

\begin{table}[ht]
\centering
\caption{Observed dataset size. A trial is a grouped prompted repetition; frames
within a trial are temporally correlated.}
\begin{tabular}{lrrl}
\toprule
Session & Frames & Grouped trials & Role \\
\midrule
S01 & 5,284 & 135 & Training \\
S02 & 3,509 & 135 & Training \\
S03 & 4,762 & 135 & Held-out evaluation \\
\midrule
Total & 13,555 & 405 & --- \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Privacy and stored schema}

All camera processing occurred locally. Original images and video were not
written to disk. Each stored CSV row represented one detected frame and
contained:
\begin{itemize}
  \item a pseudonymous participant identifier;
  \item session and trial identifiers;
  \item the prompted gesture label;
  \item frame index and relative timestamp;
  \item handedness and handedness confidence; and
  \item the $(x,y,z)$ coordinates of all 21 MediaPipe landmarks.
\end{itemize}

Landmark-only storage substantially reduces privacy exposure and dataset size,
although derived hand geometry should not be described as fully anonymous.

\section{Feature representation}

Each frame was converted into 77 numerical features. First, all landmarks were
translated so that the wrist was the origin. Coordinates were then divided by
the three-dimensional wrist-to-middle-finger-MCP distance:
\begin{equation}
\tilde{\mathbf{p}}_i =
\frac{\mathbf{p}_i-\mathbf{p}_{\mathrm{wrist}}}
{\lVert\mathbf{p}_{\mathrm{middle\ MCP}}-\mathbf{p}_{\mathrm{wrist}}\rVert_2}.
\end{equation}
This produces 63 normalized coordinate features and reduces sensitivity to hand
position and apparent size in the camera image.

Fourteen engineered features were appended:
\begin{itemize}
  \item thumb--index, thumb--middle, and index--middle fingertip distances;
  \item thumb-tip to index-MCP distance;
  \item horizontal and vertical thumb displacement;
  \item normalized index, middle, ring, and little-finger joint angles; and
  \item the four fingertip distances from the wrist.
\end{itemize}

These features reflect the geometry already considered by the rule classifier,
which makes the learned model suitable for later comparison of manual and
learned decision thresholds.

\section{Models and the decision-tree rationale}

The research tooling supports logistic regression, a random forest, and a
decision tree. All three were evaluated, but the decision tree was initially
chosen as the primary explainable model for four reasons.

\paragraph{Interpretability.}
Every prediction follows a path of explicit feature-threshold decisions. It is
therefore possible to explain why a frame was classified as a pinch or a fist
and to compare learned thresholds directly with the production rules.

\paragraph{Non-linear class boundaries.}
Gesture classes are defined by combinations of conditions rather than by a
single linear separation. A tree can naturally express statements such as a
small thumb--index distance together with a sufficiently extended index finger.

\paragraph{Little preprocessing and fast inference.}
Trees do not require feature standardization and are inexpensive enough for
real-time local inference. This is appropriate for a desktop controller.

\paragraph{Appropriate baseline complexity.}
A random forest may achieve greater robustness but is less transparent because
a prediction aggregates many trees. The purpose of this pilot was not only to
maximize accuracy, but also to retain a model whose behavior can be inspected.

The fitted tree used a maximum depth of 8, a minimum of 5 training frames
per leaf, balanced class weights, and a fixed random seed of 42. Class balancing
reduces the influence of unequal numbers of detected frames across gestures.
The random forest contained 250 trees, used a minimum of 3 frames per leaf,
balanced class weights, and the same seed. Logistic regression used standardized
features, balanced class weights, and at most 2,000 optimization iterations.
Logistic regression tests whether approximately linear class boundaries are
sufficient, while the forest tests the benefit of an ensemble of non-linear
trees at the cost of direct interpretability.

\section{Experimental design}

Each learned model was fitted on 8,793 frames from 270 trials in \texttt{S01} and
\texttt{S02}. No frame from \texttt{S03} was available during fitting. The
serialized model records its training sessions, and the comparison program
refuses to evaluate a session that overlaps with them unless the safeguard is
explicitly overridden.

For the final comparison, all four classifiers received the same 4,762 held-out
landmark frames in the same order. The production \texttt{GestureClassifier}
was reset at every trial so that its pinch hysteresis could not carry state from
one prompted repetition into another.

Two evaluation levels were used:
\begin{description}
  \item[Frame level:] every detected frame was scored separately.
  \item[Trial level:] frame predictions within a prompted trial were combined
  using majority voting, and the resulting trial prediction was scored.
\end{description}

Trial-level evaluation is primary because neighboring frames are not
independent observations and because a stable interpretation over an entire
gesture is closer to the intended interaction. Accuracy, per-class precision,
recall, F1 score, and confusion matrices were reported. Precision is the
fraction of predictions for a class that are correct; recall is the fraction of
true examples of that class that are recovered.

This experiment compares static classification only. It does not compare the
complete action pipeline, which additionally includes hold thresholds,
debouncing, swipe tracking, scrolling trajectories, and action cooldowns.

\section{Results}

\subsection{Overall performance}

\begin{table}[ht]
\centering
\caption{Held-out performance on session S03.}
\begin{tabular}{lrr}
\toprule
Classifier & Frame accuracy & Trial accuracy \\
\midrule
Random forest & \textbf{98.8\%} & \textbf{98.5\%} \\
Logistic regression & 95.7\% & 94.8\% \\
Decision tree & 91.7\% & 93.3\% \\
Hard-coded rules & 80.0\% & 79.3\% \\
\midrule
Forest--rules difference & +18.8 percentage points & +19.2 percentage points \\
\bottomrule
\end{tabular}
\end{table}

The forest classified 133 of 135 grouped trials correctly, logistic regression
approximately 128, the decision tree approximately 126, and the rules
approximately 107. Trial voting improved the tree's
accuracy relative to its frame accuracy, indicating that many tree errors were
brief rather than dominant throughout a repetition. The rule classifier did not
show the same benefit.

\subsection{Per-class performance}

\begin{table}[ht]
\centering
\caption{Decision-tree trial-level results.}
\small
\begin{tabular}{lrrrr}
\toprule
Class & Precision & Recall & F1 & Support \\
\midrule
fist & 1.00 & 0.93 & 0.97 & 15 \\
fist\_thumb\_up & 0.92 & 1.00 & 0.96 & 12 \\
none & 0.82 & 1.00 & 0.90 & 14 \\
open\_palm & 1.00 & 1.00 & 1.00 & 19 \\
pinch & 1.00 & 0.63 & 0.77 & 19 \\
pinch\_right & 0.82 & 1.00 & 0.90 & 14 \\
point & 0.92 & 1.00 & 0.96 & 11 \\
two\_finger\_scroll & 1.00 & 0.94 & 0.97 & 18 \\
v\_sign & 0.93 & 1.00 & 0.96 & 13 \\
\midrule
Macro average & 0.94 & 0.95 & 0.93 & 135 \\
Weighted average & 0.94 & 0.93 & 0.93 & 135 \\
\bottomrule
\end{tabular}
\end{table}

\begin{table}[ht]
\centering
\caption{Random-forest trial-level results.}
\small
\begin{tabular}{lrrrr}
\toprule
Class & Precision & Recall & F1 & Support \\
\midrule
fist & 1.00 & 1.00 & 1.00 & 15 \\
fist\_thumb\_up & 1.00 & 1.00 & 1.00 & 12 \\
none & 1.00 & 1.00 & 1.00 & 14 \\
open\_palm & 1.00 & 1.00 & 1.00 & 19 \\
pinch & 1.00 & 0.95 & 0.97 & 19 \\
pinch\_right & 0.93 & 1.00 & 0.97 & 14 \\
point & 0.92 & 1.00 & 0.96 & 11 \\
two\_finger\_scroll & 1.00 & 0.94 & 0.97 & 18 \\
v\_sign & 1.00 & 1.00 & 1.00 & 13 \\
\midrule
Macro average & 0.98 & 0.99 & 0.99 & 135 \\
Weighted average & 0.99 & 0.99 & 0.99 & 135 \\
\bottomrule
\end{tabular}
\end{table}

\begin{table}[ht]
\centering
\caption{Logistic-regression trial-level results.}
\small
\begin{tabular}{lrrrr}
\toprule
Class & Precision & Recall & F1 & Support \\
\midrule
fist & 1.00 & 1.00 & 1.00 & 15 \\
fist\_thumb\_up & 0.80 & 1.00 & 0.89 & 12 \\
none & 0.93 & 0.93 & 0.93 & 14 \\
open\_palm & 1.00 & 1.00 & 1.00 & 19 \\
pinch & 1.00 & 0.79 & 0.88 & 19 \\
pinch\_right & 0.88 & 1.00 & 0.93 & 14 \\
point & 0.92 & 1.00 & 0.96 & 11 \\
two\_finger\_scroll & 1.00 & 0.89 & 0.94 & 18 \\
v\_sign & 1.00 & 1.00 & 1.00 & 13 \\
\midrule
Macro average & 0.95 & 0.96 & 0.95 & 135 \\
Weighted average & 0.96 & 0.95 & 0.95 & 135 \\
\bottomrule
\end{tabular}
\end{table}

\begin{table}[ht]
\centering
\caption{Hard-coded-rule trial-level results. The rule classifier also produced
one \texttt{fist\_thumb\_left} prediction, although this class was not a target
in the collected protocol.}
\small
\begin{tabular}{lrrrr}
\toprule
Class & Precision & Recall & F1 & Support \\
\midrule
fist & 0.67 & 0.80 & 0.73 & 15 \\
fist\_thumb\_up & 0.80 & 1.00 & 0.89 & 12 \\
none & 0.00 & 0.00 & 0.00 & 14 \\
open\_palm & 0.73 & 1.00 & 0.84 & 19 \\
pinch & 0.88 & 0.79 & 0.83 & 19 \\
pinch\_right & 0.74 & 1.00 & 0.85 & 14 \\
point & 0.75 & 0.55 & 0.63 & 11 \\
two\_finger\_scroll & 1.00 & 1.00 & 1.00 & 18 \\
v\_sign & 1.00 & 0.85 & 0.92 & 13 \\
\midrule
Macro average including extra predicted class & 0.66 & 0.70 & 0.67 & 135 \\
Weighted average & 0.74 & 0.79 & 0.76 & 135 \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Confusion matrices}

For compactness, the matrices below use class abbreviations: FI (fist), TU
(thumb up), NO (none), OP (open palm), PI (index pinch), PR (middle-finger
pinch/right click), PO (point), TS (two-finger scroll), VS (V sign), and TL
(thumb left). Rows are true classes and columns are predictions.

\begin{table}[ht]
\centering
\caption{Decision-tree trial confusion matrix.}
\scriptsize
\setlength{\tabcolsep}{3.5pt}
\begin{tabular}{lrrrrrrrrr}
\toprule
 & FI & TU & NO & OP & PI & PR & PO & TS & VS \\
\midrule
FI & 14&0&1&0&0&0&0&0&0\\
TU & 0&12&0&0&0&0&0&0&0\\
NO & 0&0&14&0&0&0&0&0&0\\
OP & 0&0&0&19&0&0&0&0&0\\
PI & 0&1&2&0&12&2&1&0&1\\
PR & 0&0&0&0&0&14&0&0&0\\
PO & 0&0&0&0&0&0&11&0&0\\
TS & 0&0&0&0&0&1&0&17&0\\
VS & 0&0&0&0&0&0&0&0&13\\
\bottomrule
\end{tabular}
\end{table}

\begin{table}[ht]
\centering
\caption{Random-forest trial confusion matrix.}
\scriptsize
\setlength{\tabcolsep}{3.5pt}
\begin{tabular}{lrrrrrrrrr}
\toprule
 & FI & TU & NO & OP & PI & PR & PO & TS & VS \\
\midrule
FI &15&0&0&0&0&0&0&0&0\\
TU &0&12&0&0&0&0&0&0&0\\
NO &0&0&14&0&0&0&0&0&0\\
OP &0&0&0&19&0&0&0&0&0\\
PI &0&0&0&0&18&0&1&0&0\\
PR &0&0&0&0&0&14&0&0&0\\
PO &0&0&0&0&0&0&11&0&0\\
TS &0&0&0&0&0&1&0&17&0\\
VS &0&0&0&0&0&0&0&0&13\\
\bottomrule
\end{tabular}
\end{table}

\begin{table}[ht]
\centering
\caption{Logistic-regression trial confusion matrix.}
\scriptsize
\setlength{\tabcolsep}{3.5pt}
\begin{tabular}{lrrrrrrrrr}
\toprule
 & FI & TU & NO & OP & PI & PR & PO & TS & VS \\
\midrule
FI &15&0&0&0&0&0&0&0&0\\
TU &0&12&0&0&0&0&0&0&0\\
NO &0&0&13&0&0&1&0&0&0\\
OP &0&0&0&19&0&0&0&0&0\\
PI &0&2&0&0&15&1&1&0&0\\
PR &0&0&0&0&0&14&0&0&0\\
PO &0&0&0&0&0&0&11&0&0\\
TS &0&1&1&0&0&0&0&16&0\\
VS &0&0&0&0&0&0&0&0&13\\
\bottomrule
\end{tabular}
\end{table}

\begin{table}[ht]
\centering
\caption{Hard-coded-rule trial confusion matrix.}
\scriptsize
\setlength{\tabcolsep}{3pt}
\begin{tabular}{lrrrrrrrrrr}
\toprule
 & FI & TL & TU & NO & OP & PI & PR & PO & TS & VS \\
\midrule
FI &12&0&3&0&0&0&0&0&0&0\\
TU &0&0&12&0&0&0&0&0&0&0\\
NO &3&1&0&0&7&2&0&1&0&0\\
OP &0&0&0&0&19&0&0&0&0&0\\
PI &3&0&0&0&0&15&0&1&0&0\\
PR &0&0&0&0&0&0&14&0&0&0\\
PO &0&0&0&0&0&0&5&6&0&0\\
TS &0&0&0&0&0&0&0&0&18&0\\
VS &0&0&0&2&0&0&0&0&0&11\\
\bottomrule
\end{tabular}
\end{table}

\section{Interpretation}

\subsection{Comparison of learned models}

The random forest was the strongest classifier by a clear margin. It made only
two trial-level errors: one index-pinch trial became point, and one two-finger
scroll trial became middle-finger pinch. Ensembling reduced the instability of
the single tree, especially for index pinch, whose recall rose from 0.63 to
0.95. The trade-off is explainability: feature importance and per-prediction
methods can explain a forest, but its decisions cannot be summarized as one
short rule path.

Logistic regression ranked second, showing that the normalized and engineered
features already separate many gestures with comparatively simple boundaries.
Its remaining errors were concentrated in pinch and two-finger-scroll trials.
During fitting, the numerical backend emitted transient matrix-overflow
warnings. All input features, fitted coefficients, intercepts, and predictions
were verified as finite, and optimization completed in 78 iterations. The score
is therefore reported, but a clean-environment reproduction is advisable before
using it as a final benchmark.

The single decision tree remains the most directly interpretable learned model.
Its lower accuracy is the cost of representing the entire classification space
with one hierarchy of threshold decisions. Thus model choice depends on the
research priority: the forest is currently best for predictive performance,
while the single tree is best for direct rule-level XAI.

\subsection{Rejection of non-command movement}

The most important difference was the \texttt{none} class. The tree and forest
recovered all 14 held-out \texttt{none} trials, and logistic regression recovered
13. The rule classifier recovered none: seven
were interpreted as open palm, three as fist, two as pinch, one as point, and
one as thumb left. In a live system these errors represent potential false
commands, although the production temporal state machines may suppress some
short-lived static misclassifications.

This result suggests that a personalized model can learn not only the intended
poses but also the participant's natural non-command hand configurations. The
comparison should therefore not be summarized only as an accuracy increase;
improved rejection is the more product-relevant finding.

\subsection{Strengths and weakness of the tree}

The tree achieved perfect trial recall for thumb up, none, open palm,
middle-finger pinch, point, and V sign. It also achieved perfect precision and
recall for open palm. Its principal weakness was index pinch: precision was
1.00, but recall was only 0.63. Seven of 19 true pinch trials were assigned to
other classes: two to none, two to middle-finger pinch, and one each to thumb
up, point, and V sign. Thus the tree was conservative when emitting an index
pinch but did not create false index-pinch predictions.

This failure pattern provides a focused XAI question for further analysis:
which feature thresholds cause valid pinch frames to follow paths toward these
other leaves, and how do those thresholds compare with the manual normalized
pinch threshold?

\subsection{Strengths and weakness of the rules}

The rules performed perfectly on two-finger scroll and recovered every open
palm, thumb-up, and middle-finger-pinch trial. However, high recall sometimes
coincided with lower precision. Open palm, for example, absorbed seven
non-command trials. Point was another major weakness: only six of 11 point
trials were recovered, while five were interpreted as middle-finger pinch.

The rules encode useful domain knowledge and remain valuable as an interpretable
baseline. Their weakness in this study is not a lack of logic, but the use of
fixed boundaries that were not calibrated to this participant or to the
observed distribution of natural movement.

\section{Validity and limitations}

\begin{enumerate}
  \item \textbf{One participant.} The experiment establishes only within-user,
  across-session performance. It provides no evidence of generalization to
  other hand shapes, movement styles, skin appearances, cameras, or mobility
  characteristics.

  \item \textbf{Static classification only.} The comparison excludes the full
  temporal action pipeline. Consequently, it cannot yet show a reduction in
  actual unintended clicks or slide changes.

  \item \textbf{Correlated frames.} Thousands of frames do not represent
  thousands of independent examples. Trial-level results are therefore primary.

  \item \textbf{Trial-identifier reuse in S03.} The nominal protocol specifies
  15 trials per class, but the grouped held-out supports range from 11 to 19
  while still totaling 135. This pattern is consistent with restarting a
  randomized collection under the same session and trial identifiers, causing
  frames from differently prompted repetitions to share a grouping key. The
  frame labels remain present, but some trial-majority groups are mixed. This
  weakens the cleanliness of the trial-level estimate. A final confirmatory
  session should use a fresh session ID and must not be used to retrain or tune
  the current model.

  \item \textbf{No statistical significance test.} The report presents a
  descriptive paired comparison. Confidence intervals or a paired test should
  be added only after producing clean, uniquely identified held-out trials.

  \item \textbf{Limited model search.} Three preconfigured classical models
  were compared without hyperparameter optimization. Evaluating many settings
  against the same held-out session would itself leak test information, so S03
  must not now be used for model tuning.
\end{enumerate}

\section{Conclusion and future work}

For this participant, all three learned models generalized from two recording
sessions to a held-out third session better than the existing geometric rules.
The random forest performed best, improving trial-level accuracy by 19.2
percentage points over the rules. Logistic regression ranked second, followed
by the single decision tree. Most notably, the learned models distinguished
natural non-command motion from command gestures much more reliably. These
results support continuing with a personalized learned classifier and XAI
analysis, but they are not sufficient to replace the production rules.

The next recommended steps are:
\begin{enumerate}
  \item collect one clean confirmatory session under a new identifier;
  \item export and visualize the tree's feature importance and decision paths;
  \item inspect all misclassified pinch trials and compare learned thresholds
        with the manual pinch rules;
  \item measure false actions per minute after applying both systems' temporal
        filtering; and
  \item if more participants become available, use participant-grouped or
        leave-one-person-out evaluation.
\end{enumerate}

\appendix
\section{Reproduction commands}

Each model was trained while reserving \texttt{S03}; the model name and output
file were changed for \texttt{tree}, \texttt{forest}, and \texttt{logistic}:
\begin{lstlisting}
venv/bin/python -m research.train \
  research/data/landmarks.csv \
  --model tree \
  --exclude-session S03 \
  --output research/models/tree.joblib
\end{lstlisting}

The one-to-one comparison was then run on the held-out session:
\begin{lstlisting}
venv/bin/python -m research.compare \
  --model research/models/tree.joblib \
  --session S03 \
  research/data/landmarks.csv
\end{lstlisting}

\section{Scope of the claim}

The appropriate conclusion is: \emph{for one participant, three class-balanced
classical models trained on two sessions achieved higher static gesture-
classification accuracy than the existing geometric rules on a held-out third
session, with the random forest achieving the highest accuracy and the single
tree offering the most direct explanation}. It would be inappropriate to claim
that the models generalize
to arbitrary users or that it already improves the complete live application.

\end{document}
